\textbf{SPECFEM3D Cartesian}\\ \textbf{User Manual}

### 2016-01-03 doc/USER_MANUAL/08_doing_tomography.tex
added a reference to the users manual

We want to minimize the classical waveform misfit function:
\begin{equation}
\chi \left( \boldm \right) = \sum_{s=1}^N\sum_{r=1}^M \int_0^T \frac{1}{2} \|\boldu(\boldx_r, \boldx_s; t) - \boldd(\boldx_r, \boldx_s; t)\| ^{2} \, dt .
\label{misfit}
\end{equation}
This functional quantifies the $L^2$ difference between the observed waveforms $\boldd(\boldx_r, \boldx_s; t)$ at receivers $\boldx_r$, $r = 1, ..., M$
produced by sources at $\boldx_s$, $s=1,...,N$, and the corresponding synthetic seismograms $\boldu(\boldx_r, \boldx_s; t)$ computed in model $\boldm$.
While this misfit function is indeed classical, it is worth mentioning that in the case of noisy real data other norms could be used,
since in the oil industry for instance it is known that the $L^1$ norm
(\cite{CrPiNoMcTa90,Brossier_2010_WDR}), hybrid $L^1-L^2$ norms (\cite{Bube_1997_HL1}), Hubert norm (\cite{Ha_2009_WIU}),
Student-t distribution (\cite{ArVaHe11,Jeong_2015}) etc... can be more robust that the $L^2$ norm used here in the context of synthetic data with no noise.
In the vicinity of $\boldm$, the misfit function can be expanded into a Taylor series:
\begin{equation}
\chi(\boldm+ \delta\boldm) \approx \chi(\boldm)+\boldg(\boldm)\cdot\delta\boldm
+\delta\boldm\cdot\mathbf{H}(\boldm)\cdot\delta\boldm \, ,
\label{local_misfit}
\end{equation}
where $\boldg(\boldm)$ is the gradient of the waveform misfit function:
\begin{equation}
\boldg(\boldm) = \frac{\partial\chi(\boldm)}{\partial\boldm} \, ,
\end{equation}
and $\mathbf{H}(\boldm)$ the Hessian:
\begin{equation}
\mathbf{H}(\boldm) = \frac{\partial^2\chi(\boldm)}{\partial\boldm^2} \, .
\end{equation}
In the following, for simplicity the dependence of the gradient and Hessian on the model will be implicitly assumed and omitted in the notations.
The nearest minimum of $\chi$ in (\ref{local_misfit}) with respect to the model perturbation $\delta \boldm$ is reached for
\begin{equation}
\delta \boldm = -\mathbf{H}^{-1} \cdot \boldg \, .
\label{Newton}
\end{equation}
The local minimum of (\ref{misfit}) is thus given by perturbing the model in the direction of the gradient preconditioned
by the inverse Hessian.

>>>>

We want to minimize the classical waveform misfit function:
\begin{equation}
\chi \left( \boldm \right) = \sum_{s=1}^N\sum_{r=1}^M \int_0^T \frac{1}{2} \|\boldu(\boldx_r, \boldx_s; t) - \boldd(\boldx_r, \boldx_s; t)\| ^{2} \, dt .
\label{misfit}
\end{equation}
This functional quantifies the $L^2$ difference between the observed waveforms $\boldd(\boldx_r, \boldx_s; t)$ at receivers $\boldx_r$, $r = 1, ..., M$
produced by sources at $\boldx_s$, $s=1,...,N$, and the corresponding synthetic seismograms $\boldu(\boldx_r, \boldx_s; t)$ computed in model $\boldm$.
While this misfit function is indeed classical, it is worth mentioning that in the case of noisy real data other norms could be used,
since in the oil industry for instance it is known that the $L^1$ norm
(\cite{CrPiNoMcTa90,BrOpVi2010}), hybrid $L^1-L^2$ norms (\cite{Bube_1997_HL1}), Hubert norm (\cite{Ha_2009_WIU}),
Student-t distribution (\cite{ArVaHe11,Jeong_2015}) etc... can be more robust that the $L^2$ norm used here in the context of synthetic data with no noise.
In the vicinity of $\boldm$, the misfit function can be expanded into a Taylor series:
\begin{equation}
\chi(\boldm+ \delta\boldm) \approx \chi(\boldm)+\boldg(\boldm)\cdot\delta\boldm
+\delta\boldm\cdot\mathbf{H}(\boldm)\cdot\delta\boldm \, ,
\label{local_misfit}
\end{equation}
where $\boldg(\boldm)$ is the gradient of the waveform misfit function:
\begin{equation}
\boldg(\boldm) = \frac{\partial\chi(\boldm)}{\partial\boldm} \, ,
\end{equation}
and $\mathbf{H}(\boldm)$ the Hessian:
\begin{equation}
\mathbf{H}(\boldm) = \frac{\partial^2\chi(\boldm)}{\partial\boldm^2} \, .
\end{equation}
In the following, for simplicity the dependence of the gradient and Hessian on the model will be implicitly assumed and omitted in the notations.
The nearest minimum of $\chi$ in (\ref{local_misfit}) with respect to the model perturbation $\delta \boldm$ is reached for
\begin{equation}
\delta \boldm = -\mathbf{H}^{-1} \cdot \boldg \, .
\label{Newton}
\end{equation}
The local minimum of (\ref{misfit}) is thus given by perturbing the model in the direction of the gradient preconditioned
by the inverse Hessian.
